BIP-Predictor

### 2025-05-10 Sweave/BIP_predictor.Rnw
up

par(mfrow=c(1,2))
colo<-c("black", "red", "green", "blue", "orange", "dimgray")
mplot<-gammak
plot(mplot[,1],main="M-MSE",axes=F,type="l",xlab="",ylab="",col=colo[1],ylim=c(min(na.exclude(mplot)),max(na.exclude(mplot))))

@@

par(mfrow=c(1,2))
colo<-c("black", "red", "green", "blue", "orange", "dimgray")
mplot<-bk
plot(mplot[,1],main="M-SSA: h=0",axes=F,type="l",xlab="",ylab="",col=colo[1],ylim=c(min(na.exclude(mplot)),max(na.exclude(mplot))))

@@

  mplot<-mplot[which(rownames(mplot)>2006&rownames(mplot)<2011),]
  colnames(mplot)<-c("BIP","M-SSA","HP-C")
  colo<-c("black","blue","red")
  main_title<-paste("GDP shifted forward by ",h," quarters",sep="")
  plot(mplot[,1],main=main_title,axes=F,type="l",xlab="",ylab="",col=colo[1],ylim=c(min(na.exclude(mplot)),max(na.exclude(mplot))))
  for (i in 1:ncol(mplot))
  {
    lines(mplot[,i],col=colo[i])
#    mtext(colnames(mplot)[i],col=colo[i],line=-i)
  }
  abline(h=0)
  axis(1,at=1:nrow(mplot),labels=rownames(mplot))
  axis(2)
  if (h==3)
    legend("bottomleft", legend = colnames(mplot), col = colo, lty = 1, lwd = 1, bty = "n")

@@

par(mfrow=c(1,1))
mplot<-cbind(x_mat[,"BIP"],predictor_mssa_mat)
rownames(mplot)<-rownames(x_mat)
mplot<-mplot[L:nrow(mplot),]
colo<-c("black",rainbow(ncol(mplot)-1))
colnames(mplot)[1]<-"BIP"
main_title<-"Equally-weighted average of M-SSA outputs"
plot(mplot[,1],main=main_title,axes=F,type="l",xlab="",ylab="",col=colo[1],ylim=c(min(na.exclude(mplot)),max(na.exclude(mplot))))
#mtext(colnames(mplot)[1],col=colo[1],line=-1)
for (j in 1:ncol(mplot))
{
  lines(mplot[,j],col=colo[j],lwd=1,lty=1)
#  mtext(colnames(mplot)[j],col=colo[j],line=-j)
}
abline(h=0)
axis(1,at=1:nrow(mplot),labels=rownames(mplot))
axis(2)
legend("bottomleft", legend = colnames(mplot), col = colo, lty = 1, lwd = 1, bty = "n")

@@

j_now<-1
# Plot M-SSA nowcast and components
par(mfrow=c(1,1))
# Scale the data 
mplot<-scale(cbind(predictor_mssa_mat[,j_now],scale(t(mssa_array[,,j_now]))))
rownames(mplot)<-rownames(x_mat)
colnames(mplot)<-c(paste("M-SSA predictor optimized for h=",h_vec[j_now],sep=""),
                   paste("Subseries ",select_vec_multi,sep=""))
mplot<-mplot[L:nrow(mplot),]
colo<-c("blue","black", "red", "green", "blue", "orange", "dimgray")

@@

# Plot MA inversions
file = "./Figures/up_dated_ma_inv_multi_ip.pdf"
pdf(file = paste(path.out,file,sep=""), paper = "special", width = 7, height = 7)
colo<-c("black", "red", "green", "blue", "orange", "dimgray")
# Select BIP component
ih<-1
par(mfrow=c(1,2))
# 2008
xi<-compute_xi_func(V_obj_2008,L)$xi
mplot<-xi[ih,1:min(10,L)]
for (j in 2:n)
{
  mplot<-cbind(mplot,xi[ih,(j-1)*L+1:min(10,L)])
}
colnames(mplot)<-select_vec_multi
plot(mplot[,1],main=paste("MA inversion GDP: 2008",sep=""),axes=F,type="l",xlab="",ylab="",col=colo[1],ylim=c(min(na.exclude(mplot)),max(na.exclude(mplot))))

@@

par(mfrow=c(1,2))
mplot<-bk_2008
ts.plot(mplot,col=colo,main=paste("M-SSA data up to 2008: h=",h,sep=""),xlab="")
#for (i in 1:ncol(mplot))
#  mtext(colnames(mplot)[i],col=colo[i],line=-i)
legend("topright", legend = colnames(mplot), col = colo, lty = 1, lwd = 1, bty = "n")
mplot<-bk_all
ts.plot(mplot,col=colo,main="Full data set",xlab="")
#for (i in 1:ncol(mplot))
#  mtext(colnames(mplot)[i],col=colo[i],line=-i)

>>>>

par(mfrow=c(1,2))
colo<-c("black", "red", "green", "blue", "orange", "dimgray")
mplot<-gammak
colnames(mplot)[1]<-"GDP"
plot(mplot[,1],main="M-MSE",axes=F,type="l",xlab="",ylab="",col=colo[1],ylim=c(min(na.exclude(mplot)),max(na.exclude(mplot))))

@@

par(mfrow=c(1,2))
colo<-c("black", "red", "green", "blue", "orange", "dimgray")
mplot<-bk
colnames(mplot)[1]<-"GDP"
plot(mplot[,1],main="M-SSA: h=0",axes=F,type="l",xlab="",ylab="",col=colo[1],ylim=c(min(na.exclude(mplot)),max(na.exclude(mplot))))

@@

  mplot<-mplot[which(rownames(mplot)>2006&rownames(mplot)<2011),]
  colnames(mplot)<-c("GDP","M-SSA","HP-C")
  colo<-c("black","blue","red")
  main_title<-paste("GDP shifted forward by ",h," quarters",sep="")
  plot(mplot[,1],main=main_title,axes=F,type="l",xlab="",ylab="",col=colo[1],ylim=c(min(na.exclude(mplot)),max(na.exclude(mplot))))
  for (i in 1:ncol(mplot))
  {
    lines(mplot[,i],col=colo[i])
#    mtext(colnames(mplot)[i],col=colo[i],line=-i)
  }
  abline(h=0)
  axis(1,at=1:nrow(mplot),labels=rownames(mplot))
  axis(2)
  if (h==3)
    legend("bottomleft", legend = colnames(mplot), col = colo, lty = 1, lwd = 1, bty = "n")

@@

par(mfrow=c(1,1))
mplot<-cbind(x_mat[,"BIP"],predictor_mssa_mat)
rownames(mplot)<-rownames(x_mat)
mplot<-mplot[L:nrow(mplot),]
colo<-c("black",rainbow(ncol(mplot)-1))
colnames(mplot)[1]<-"GDP"
main_title<-"Equally-weighted average of M-SSA outputs"
plot(mplot[,1],main=main_title,axes=F,type="l",xlab="",ylab="",col=colo[1],ylim=c(min(na.exclude(mplot)),max(na.exclude(mplot))))
#mtext(colnames(mplot)[1],col=colo[1],line=-1)
for (j in 1:ncol(mplot))
{
  lines(mplot[,j],col=colo[j],lwd=1,lty=1)
#  mtext(colnames(mplot)[j],col=colo[j],line=-j)
}
abline(h=0)
axis(1,at=1:nrow(mplot),labels=rownames(mplot))
axis(2)
legend("bottomleft", legend = colnames(mplot), col = colo, lty = 1, lwd = 1, bty = "n")

@@

j_now<-1
# Plot M-SSA nowcast and components
par(mfrow=c(1,1))
# Scale the data 
mplot<-scale(cbind(predictor_mssa_mat[,j_now],scale(t(mssa_array[,,j_now]))))
rownames(mplot)<-rownames(x_mat)
colnames(mplot)<-c(paste("M-SSA predictor optimized for h=",h_vec[j_now],sep=""),
                   paste("Subseries ",select_vec_multi,sep=""))
mplot<-mplot[L:nrow(mplot),]
colo<-c("blue","black", "red", "green", "blue", "orange", "dimgray")
colnames(mplot)[2]<-"Subseries GDP"

@@

# Plot MA inversions
file = "./Figures/up_dated_ma_inv_multi_ip.pdf"
pdf(file = paste(path.out,file,sep=""), paper = "special", width = 7, height = 7)
colo<-c("black", "red", "green", "blue", "orange", "dimgray")
# Select BIP component
ih<-1
par(mfrow=c(1,2))
# 2008
xi<-compute_xi_func(V_obj_2008,L)$xi
mplot<-xi[ih,1:min(10,L)]
for (j in 2:n)
{
  mplot<-cbind(mplot,xi[ih,(j-1)*L+1:min(10,L)])
}
colnames(mplot)<-select_vec_multi
colnames(mplot)[1]<-"GDP"
plot(mplot[,1],main=paste("MA inversion GDP: 2008",sep=""),axes=F,type="l",xlab="",ylab="",col=colo[1],ylim=c(min(na.exclude(mplot)),max(na.exclude(mplot))))

@@

par(mfrow=c(1,2))
mplot<-bk_2008
colnames(mplot)[1]<-"GDP"
ts.plot(mplot,col=colo,main=paste("M-SSA data up to 2008: h=",h,sep=""),xlab="")
#for (i in 1:ncol(mplot))
#  mtext(colnames(mplot)[i],col=colo[i],line=-i)
legend("topright", legend = colnames(mplot), col = colo, lty = 1, lwd = 1, bty = "n")
mplot<-bk_all
ts.plot(mplot,col=colo,main="Full data set",xlab="")
#for (i in 1:ncol(mplot))
#  mtext(colnames(mplot)[i],col=colo[i],line=-i)
